Molecular dynamics simulation of synchronization of a driven particle

### 2021-04-12 manuscript/manuscript_ajp_version3.tex
rejiggered the introduction following, main topic, define, illustrate, transition

%Single oscillators 
%can demonstrate a variety of synchronized behaviors.
Colloid particles in complex environments are an excellent
model system to explore %these 
the dynamics of mode-locking. %synchronization.
In experiments %DM moved the ``in experiments'' to second sentence
typical colloids are   
plastic spheres suspended in
de-ionized water or silica beads suspended in organic solvent.
Colloids can be trapped
with 
radiation pressure from 
a laser beam.\cite{Ashkin1997} 
A colloid in such a confining region,
an optical trap, oscillates
about a equilibrium point.
A colloid centered in an optical trap is 
uniformly bombarded by photons. 
Off-center colloids 
experience a net force
due to uneven photon collisions across
the particle surface.
Depending on the 
location of the particle in the trap,
the radiation pressure either moves colloids toward the center 
or ejects it from the trap.

% such as synchronized mode-locking can be studied with
%An advantage of colloid studies
While many systems oscillate,
trapped colloids are useful for 
providing controlled 
measurements of the
step-by-step dynamics of particle motion.
Colloids are large 
and move slowly so
%colloids are considered model systems
particle positions 
can be measured in real time 
with an optical camera.\cite{Pertsinidis2001}
Colloids have been
shown to 
provide an ideal system to 
control and study
phase-locked motions
%are useful for
%understanding synchronization
at a single particle level.\cite{Juniper2015,Juniper2017}
%Light is a
%tool for manipulating the colloidal environment,
%which can alter synchronization patterns.
%Synchronization patterns can be altered
%using light to manipulate
%the colloidal environment.
Diffraction gratings can create
more complex light environments, 
such as periodic patterns of minima
suitable for synchronization studies.\cite{Grier2003}
In the following study,
we assume the colloids are confined
to move along a periodic light pattern
with minima and maxima defined by a sine wave.

>>>>

%Single oscillators 
%can demonstrate a variety of synchronized behaviors.
Colloid particles in complex environments are an excellent
model system to explore %these 
the dynamics of mode-locking. %synchronization.
In experiments %DM moved the ``in experiments'' to second sentence
typical colloids are   
plastic spheres suspended in
de-ionized water or silica beads suspended in organic solvent.
Colloids can be trapped
with 
radiation pressure from 
a laser beam.\cite{Ashkin1997} 
A colloid in such a confining region,
an optical trap, oscillates
about a equilibrium point.
A colloid centered in an optical trap is 
uniformly bombarded by photons. 
Off-center colloids 
experience a net force
due to uneven photon collisions across
the particle surface.
Depending on the 
location of the particle in the trap,
the radiation pressure either moves colloids toward the center 
or ejects it from the trap.
Diffraction gratings can create
more complex light environments, 
such as periodic patterns of minima
suitable for synchronization studies.\cite{Grier2003}
A driven colloid
can demonstrate
synchronized
motion within one trap,
or synchronized hopping between multiple traps.

Colloids have been
shown to 
provide an ideal system to 
control and study
phase-locked motions
%are useful for
%understanding synchronization
at a single particle level.\cite{Juniper2015,Juniper2017}
% such as synchronized mode-locking can be studied with
%An advantage of colloid studies
While many systems oscillate,
trapped colloids are useful for 
providing controlled 
measurements of the
step-by-step dynamics of particle motion.
Since
colloids are large 
and move slowly, 
%colloids are considered model systems
particle positions 
can be measured in real time 
with an optical camera.\cite{Pertsinidis2001}
%Light is a
%tool for manipulating the colloidal environment,
%which can alter synchronization patterns.
%Synchronization patterns can be altered
%using light to manipulate
%the colloidal environment.
Simulations provide complementary
information,
where environmental and driving parameters may be precisely
and quickly modified to explore
the many oscillation patterns.
%the dynamics from external
In the following study,
we confine colloids  
to move along a periodic light pattern
with minima and maxima defined by a sine wave,
a washboard potential energy substrate.
